Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-02-06 paper_comparison/paper_comparison/paper_comparison.Rmd
add 1000 boot smooth lines for uniform (5)

```{r}
vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(reject_only_5  = as.numeric(p_value_only_5 < 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject), 
              method = "glm", 
              method.args = list(family = binomial()),
              se = FALSE) +
  geom_smooth(aes(log_effect_size, reject_only_5), 
              method = "glm", 
              method.args = list(family = binomial()),
              col = "red",
              se = FALSE) +
  facet_wrap(~type)
```

@@

  vi_survey %>%
    filter(!null_lineup) %>%
    filter(!attention_check) %>%
    group_by(unique_lineup_id) %>%
    summarise(across(everything(), first)) %>%
    mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
    mutate(reject = as.numeric(p_value <= 0.05)) %>%
    mutate(log_effect_size = log(effect_size)) %>%
    mutate(x_dist = ifelse(x_dist == "even_discrete", 
                           "Discrete", 
                           stringr::str_to_title(x_dist))) %>%
    mutate(conv_or_not = "Visual") %>%
    select(type, x_dist, log_effect_size, reject, conv_or_not)
) %>%

@@

@@

  # Bold the uniform smooth line
  # geom_smooth(data = ~filter(.x, x_dist == "Uniform"),
  #             aes(log_effect_size, reject), 
  #             col = "grey", 
  #             se = FALSE, 
  #             span = 0.03,
  #             size = 3) +

  # Draw all smooth lines
  geom_smooth(data = ~filter(.x, x_dist != "Uniform"),
              aes(log_effect_size, reject, col = x_dist), 
              span = 0.03,
              se = FALSE, 
              size = 1) +

  geom_smooth(data = vi_survey %>%
                filter(!null_lineup) %>%
                filter(!attention_check) %>%
                filter(x_dist == "uniform") %>%
                group_by(unique_lineup_id) %>%
                summarise(across(everything(), first)) %>%
                mutate(reject = as.numeric(p_value < 0.05)) %>%
                mutate(reject_only_5  = as.numeric(p_value_only_5 < 0.05)) %>%
                mutate(log_effect_size = log(effect_size)) %>%
                mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
                mutate(conv_or_not = "Visual"),
              aes(log_effect_size, reject_only_5, col = "Uniform"),
              method = "glm",
              method.args = list(family = binomial()),
              se = FALSE
              ) +

>>>>

```{r get-5-eval, cache = TRUE}
dat_uniform_5 <- map_df(1:1000, function(boot_id) {
  vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  slice_sample(n = 5) %>%
  ungroup() %>%
  calc_p_value_multi(lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha) %>%
  mutate(boot_id = boot_id)
}) %>%
  left_join(select(vi_survey, unique_lineup_id, effect_size, x_dist, type)) %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(conv_or_not = "Visual") %>%
  select(-unique_lineup_id, -p_value, -effect_size)

```

@@

  vi_survey %>%
    filter(!null_lineup) %>%
    filter(!attention_check) %>%
    group_by(unique_lineup_id) %>%
    summarise(across(everything(), first)) %>%
    filter(x_dist != "uniform") %>%
    mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
    mutate(reject = as.numeric(p_value <= 0.05)) %>%
    mutate(log_effect_size = log(effect_size)) %>%
    mutate(x_dist = ifelse(x_dist == "even_discrete", 
                           "Discrete", 
                           stringr::str_to_title(x_dist))) %>%
    mutate(conv_or_not = "Visual") %>%
    select(type, x_dist, log_effect_size, reject, conv_or_not)
) %>%

@@

dat_uniform_5_pred <- dat_uniform_5 %>%
  mutate(es_min = min(dat_x_dist$log_effect_size), 
         es_max = max(dat_x_dist$log_effect_size)) %>%
  nest(data = c(log_effect_size, reject)) %>%
  mutate(mod = map(data, 
                   ~glm(reject ~ log_effect_size, 
                        family = binomial(), 
                        data = .x))) %>%
  mutate(reject = map(mod, function(mod) {
    result <- data.frame(log_effect_size = seq(es_min[1], es_max[1], 0.01))
    result$reject <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-es_min, -es_max, -data, -mod) %>%
  unnest(reject)

@@

  # Draw all smooth lines
  geom_smooth(aes(log_effect_size, reject, col = x_dist),
              span = 0.03,
              se = FALSE,
              size = 1) +

  # Draw boot uniform (5 eval) lines
  stat_smooth(data = dat_uniform_5_pred,
              geom = "line",
              aes(log_effect_size, reject, col = "Uniform", group = boot_id),
              span = 0.03,
              se = FALSE,
              alpha = 0.01) +

### 2023-02-06 paper_comparison/paper_comparison/paper_comparison.tex
add 1000 boot smooth lines for uniform (5)

Three experiments are conducted to investigate the difference between
conventional hypothesis testing and visual inference in the application
of linear regression diagnostics. Two types of departures, namely
non-linearity and heteroskedasticity, are considered with the
corresponding data generating process being designed for experiment I
and II. The experiment III is designed for collecting human responses to
null lineups such that the parameter \(\alpha\) in Equation
\ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to
collect 7974 evaluations on 1152 unique lineups performed by 443
subjects throughout three experiments.

@@

Experiment I is designed to study the ability of human subjects to
detect the effect of a non-linear term \(\boldsymbol{z}\) constructed
using Hermite polynomials on random vector \(\boldsymbol{x}\) formulated
as

@@

\caption{\label{tab:model-factor-table}Levels of the factors used in experiments I, II, III.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rr|rr|rcrr|rr|rcrr|rr|rcrr|rr|rcrr|rr|rcrr|rr|rc}
\toprule
\multicolumn{2}{c}{Non-linearity} & \multicolumn{2}{c}{Heteroskedasticity} & \multicolumn{2}{c}{Common} \\
\cmidrule(l{3pt}r{3pt}){1-2} \cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6}
\multicolumn{1}{c}{Poly Order ($j$)} & \multicolumn{1}{c}{SD ($\sigma$)} & \multicolumn{1}{c}{Shape ($a$)} & \multicolumn{1}{c}{Ratio ($b$)} & \multicolumn{1}{c}{Size ($n$)} & \multicolumn{1}{c}{Distribution of fitted values} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
2 & 0.25 & -1 & 0.25 & 50 & Uniform\\
3 & 1.00 & 0 & 1.00 & 100 & Normal\\
6 & 2.00 & 1 & 4.00 & 300 & Skewed\\
18 & 4.00 &  & 16.00 &  & Discrete uniform\\
 &  &  & 64.00 &  & \\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{Polynomial forms generated for the residual plots used in experiment I. The four shapes are generated by varying the order of polynomial given by $j$ in $He_j(.)$.}\label{fig:different-shape-of-herimite}
\end{figure}

@@

Figure \ref{fig:example-poly-lineup} demonstrates one of the lineups
used in experiment I. This lineup is produced by the non-linearity model
with \(j = 6\) and uniform fitted values. The data plot location is
\(2^3 - 4\). All five subjects correctly identify the data plot from
this lineup.

@@

\caption{Number of observations $n$ have an impact on the strength of the signal. Three different values of $n$ are used in experiment I, II and III.}\label{fig:different-n}
\end{figure}

@@

\caption{For the non-lienearity model, the standard deviation of the error term $\sigma$ affects the strength of the signal. Four different values of $\sigma$ are used in the experiment I.}\label{fig:different-sigma}
\end{figure}

@@

\caption{One of the lineups containing non-linearity patterns used in experiment I. Can you spot the most different plot? The data plot is positioned at $2^3 + 1$.}\label{fig:example-poly-lineup}
\end{figure}

@@

\caption{Heteroskedasticity forms used in experiment II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes.}\label{fig:different-shape-of-heter}
\end{figure}

@@

\caption{Five different values of $b$ are used in experiment II to control the strength of the signal.}\label{fig:different-b}
\end{figure}

@@

\caption{One of the lineups containing heteroskedasticity pattern used in experiment II. Can you spot the most different plot? The data plot is positioned at $3^3 - 3^2$}\label{fig:example-heter-lineup}
\end{figure}

An example lineup of this model used in Experiment II is shown in Figure
\ref{fig:example-heter-lineup} with \(a = -1\) and
\(X_{raw} \sim U(-1, 1)\). The data plot location is \(2^4 + 2\). Nine
out of 11 subjects correctly identify the data plot from this lineup.

\hypertarget{factors-common-to-both-experiments}{%
\subsubsection{Factors common to both
experiments}\label{factors-common-to-both-experiments}}

@@

As summarised in Table \ref{tab:model-factor-table}, three additional
parameters \(n\), \(\sigma\) and \(b\) are used to control the strength
of the signal so that different difficulty levels of lineups are
generated, and therefore, the estimated power curve will be smooth and
continuous. Parameter \(\sigma \in \{0.5, 1, 2, 4\}\) and
\(b \in \{0.25, 1, 4, 16, 64\}\) are used in experiment I and II
respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b}
demonstrate the impact of these two parameters. A large value of
\(\sigma\) will increase the variation of the error of the non-linearity
model and decrease the visibility of the visual pattern. The parameter
\(b\) controls the standard deviation of the error across the support of
the regressor. Given \(x \neq a\), a larger value of \(b\) will lead to
a larger ratio of the variance at \(x\) to the variance at
\(x - a = 0\), making the visual pattern more obvious.

Three different sample sizes are used (n = 50, 100, 300) in all three
experiments. It can be observed from Figure \ref{fig:different-n} that
with fewer data points drawn in a residual plot, the visual pattern is
more difficult to be detected.

@@

Three replications are made for each of the parameter values shown in
Table \ref{tab:model-factor-table} resulting in
\((4 \times 4 \times 4 \times 3 + 4 \times 3 \times 5 \times 3) \times 3 = 1116\)
different lineups. In addition, each lineup is designed to be evaluated
by five different subjects. After attempting some pilot studies
internally in our research group, we decide to present a block of 20
lineups to every subject. And to ensure the quality of the survey data,
two lineups with obvious visual patterns are included as attention
checks. Thus, \(576 \times 5 / (20-2) = 160\) and
\(540 \times 5 / (20-2) = 150\) subjects are recruited to satisfy the
design of the experiment I and experiment II respectively.

As mentioned in Section \ref{calculating-p-values-for-the-visual-test},
\(\alpha\) used in Equation \ref{eq:pvalue-beta-binomial} needs to be
estimated using null lineups. Hence, three replications of 36 lineups
with all combinations of \(n\) and fitted value distributions are
included in experiment III. In these lineups, the data of the data plot
is generated from a model with zero effect size, while the data of the
19 null plots are generated using the same simulation method discussed
in Section \ref{sampling-from-the-null-distribution}. This generation
procedure differs from the canonical Rorschach lineup procedure, which
requires that all 20 plots are generated from the null hypothesis.
However, these lineups serve the same fundamental purpose: to assess the
number of visually interesting plots generated under the null
hypothesis.

@@

All lineups consist of only null plots are planned to be evaluated by 20
subjects. However, presenting only these lineups to subjects are
considered to be bad practices as subjects will lose interest quickly.
Therefore, we plan to collect 6 more evaluations on the 279 lineups with
uniform fitted values, result in
\((36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3 \times 6) / (20-2) = 133\)
subjects recruited for experiment III.

@@

Subjects for all three experiments are recruited from an crowdsourcing
platform called Prolific \citep{palan2018prolific}. Prescreening
procedure is applied during the recruitment, subjects are required to be
fluent in English, with \(98\%\) minimum approval rate and 10 minimum
submissions in other studies.

@@

There are 2880, 2700 and 1674 lineups evaluation made by 160, 150 and
133 subjects recruited for experiment I, II and III respectively. In the
total of 7974 lineup evaluations, 3744 use lineups produced by the
non-linearity model, and 4230 use lineups produced by the
heteroskedasticity model. Besides, there are 886 attention checks and
720 evaluations on null lineups needed for the estimate of \(\alpha\)
not included in the analysis. The collated dataset is provided in
\texttt{vi\_survey} of the \texttt{visage} \texttt{R} package.

@@

\caption{Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. Each power curve of the uniform distribution is surrounded by a grey line to indicate it is the baseline in its group. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power for non-linearity patterns in residual plots. For heteroskedasticity patterns, normal and lognormal distributions produce lower power.}\label{fig:different-x-dist-poly-power}
\end{figure}

@@

This paper has demonstrated that conventional residual-based statistical
tests are more sensitive to departures from assumptions for residuals
than visual tests evaluated by humans in the diagnostics of linear
regression models. Three experiments are conducted with two simulation
models designed for non-linearity and heteroskedasticity model defects
being applied. Methods for obtaining the \(p\)-value of visual tests
proposed by \citet{vanderplas2021statistical} are extended to allowed
for multiple selections in a lineup protocol.

@@

Throughout the three human subject experiments we conducted, residual
plots rejected by visual tests are rarely not rejected by conventional
tests, but departures of residuals that are of little practical sense to
humans will often be alarmed by conventional tests, supporting the
common guidance given by experts to utilize graphical representations of
data in model diagnostics.

We have also found that residual-based conventional tests relying on a
user-parameterized test formula, such as the RESET test, will suffer
from a decrease in power for detecting certain residual departures
intended to be tested but not covered by the test formula. This can not
be avoided without prior knowledge of their functional forms, which is
usually obtained by plotting the residuals. On the other hand, visual
tests do not rely on such information and a collection of departures can
be tested simultaneously.

Besides, fitted value distributions

with different

symmetric, evenly

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  how does this apply more broadly than simple regression
\item
  where does this lead? Computer vision residual plot reading
\end{enumerate}

@@

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  experiments -\textgreater{} data collection periods
\end{enumerate}

To investigate the difference between conventional hypothesis testing
and visual inference in the application of linear regression
diagnostics, an experiment is conducted in three data collection
periods. Two types of departures, namely non-linearity and
heteroskedasticity, are considered with the corresponding data
generating process being designed for data collection periods I and II.
The data collection period III is designed for collecting human
responses to null lineups such that the parameter \(\alpha\) in Equation
\ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to
collect 7974 evaluations on 1152 unique lineups performed by 443
subjects throughout three data collection periods.

@@

Data collection period I is designed to study the ability of human
subjects to detect the effect of a non-linear term \(\boldsymbol{z}\)
constructed using Hermite polynomials on random vector
\(\boldsymbol{x}\) formulated as

@@

\caption{\label{tab:model-factor-table}Levels of the factors used in data collection periods I, II, III.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rr|rr|rcrr|rr|rcrr|rr|rcrr|rr|rcrr|rr|rcrr|rr|rc}
\toprule
\multicolumn{2}{c}{Non-linearity} & \multicolumn{2}{c}{Heteroskedasticity} & \multicolumn{2}{c}{Common} \\
\cmidrule(l{3pt}r{3pt}){1-2} \cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6}
\multicolumn{1}{c}{Poly Order ($j$)} & \multicolumn{1}{c}{SD ($\sigma$)} & \multicolumn{1}{c}{Shape ($a$)} & \multicolumn{1}{c}{Ratio ($b$)} & \multicolumn{1}{c}{Size ($n$)} & \multicolumn{1}{c}{Distribution of fitted values} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
2 & 0.25 & -1 & 0.25 & 50 & Uniform\\
3 & 1.00 & 0 & 1.00 & 100 & Normal\\
6 & 2.00 & 1 & 4.00 & 300 & Skewed\\
18 & 4.00 &  & 16.00 &  & Discrete uniform\\
 &  &  & 64.00 &  & \\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{Polynomial forms generated for the residual plots used in data collection period I. The four shapes are generated by varying the order of polynomial given by $j$ in $He_j(.)$.}\label{fig:different-shape-of-herimite}
\end{figure}

@@

Figure \ref{fig:example-poly-lineup} demonstrates one of the lineups
used in data collection period I. This lineup is produced by the
non-linearity model with \(j = 6\) and uniform fitted values. The data
plot location is \(2^3 - 4\). All five subjects correctly identify the
data plot from this lineup.

@@

\caption{Number of observations $n$ have an impact on the strength of the signal. Three different values of $n$ are used in data collection periods I, II and III.}\label{fig:different-n}
\end{figure}

@@

\caption{For the non-lienearity model, the standard deviation of the error term $\sigma$ affects the strength of the signal. Four different values of $\sigma$ are used in the data collection period I.}\label{fig:different-sigma}
\end{figure}

@@

\caption{One of the lineups containing non-linearity patterns used in data collection period I. Can you spot the most different plot? The data plot is positioned at $2^3 + 1$.}\label{fig:example-poly-lineup}
\end{figure}

@@

\caption{Heteroskedasticity forms used in data collection period II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes.}\label{fig:different-shape-of-heter}
\end{figure}

@@

\caption{Five different values of $b$ are used in data collection period II to control the strength of the signal.}\label{fig:different-b}
\end{figure}

@@

\caption{One of the lineups containing heteroskedasticity pattern used in data collection period II. Can you spot the most different plot? The data plot is positioned at $3^3 - 3^2$}\label{fig:example-heter-lineup}
\end{figure}

An example lineup of this model used in data collection period II is
shown in Figure \ref{fig:example-heter-lineup} with \(a = -1\) and
\(X_{raw} \sim U(-1, 1)\). The data plot location is \(2^4 + 2\). Nine
out of 11 subjects correctly identify the data plot from this lineup.

\hypertarget{factors-common-to-both-data-collection-periods}{%
\subsubsection{Factors common to both data collection
periods}\label{factors-common-to-both-data-collection-periods}}

@@

As summarised in Table \ref{tab:model-factor-table}, three additional
parameters \(n\), \(\sigma\) and \(b\) are used to control the strength
of the signal so that different difficulty levels of lineups are
generated, and therefore, the estimated power curve will be smooth and
continuous. Parameter \(\sigma \in \{0.5, 1, 2, 4\}\) and
\(b \in \{0.25, 1, 4, 16, 64\}\) are used in data collection periods I
and II respectively. Figure \ref{fig:different-sigma} and
\ref{fig:different-b} demonstrate the impact of these two parameters. A
large value of \(\sigma\) will increase the variation of the error of
the non-linearity model and decrease the visibility of the visual
pattern. The parameter \(b\) controls the standard deviation of the
error across the support of the regressor. Given \(x \neq a\), a larger
value of \(b\) will lead to a larger ratio of the variance at \(x\) to
the variance at \(x - a = 0\), making the visual pattern more obvious.

Three different sample sizes are used (n = 50, 100, 300) in all three
data collection periods. It can be observed from Figure
\ref{fig:different-n} that with fewer data points drawn in a residual
plot, the visual pattern is more difficult to be detected.

@@

Three replications are made for each of the parameter values shown in
Table \ref{tab:model-factor-table} resulting in
\((4 \times 4 \times 4 \times 3 + 4 \times 3 \times 5 \times 3) \times 3 = 1116\)
different lineups. In addition, each lineup is designed to be evaluated
by five different subjects. After attempting some pilot studies
internally in our research group, we decide to present a block of 20
lineups to every subject. And to ensure the quality of the survey data,
two lineups with obvious visual patterns are included as attention
checks. Thus, \(576 \times 5 / (20-2) = 160\) and
\(540 \times 5 / (20-2) = 150\) subjects are recruited to satisfy the
design of the data collection period I and II respectively.

As mentioned in Section \ref{calculating-p-values-for-the-visual-test},
\(\alpha\) used in Equation \ref{eq:pvalue-beta-binomial} needs to be
estimated using null lineups. Hence, three replications of 36 lineups
with all combinations of \(n\) and fitted value distributions are
included in data collection period III. In these lineups, the data of
the data plot is generated from a model with zero effect size, while the
data of the 19 null plots are generated using the same simulation method
discussed in Section \ref{sampling-from-the-null-distribution}. This
generation procedure differs from the canonical Rorschach lineup
procedure, which requires that all 20 plots are generated from the null
hypothesis. However, these lineups serve the same fundamental purpose:
to assess the number of visually interesting plots generated under the
null hypothesis.

@@

All lineups consist of only null plots are planned to be evaluated by 20
subjects. However, presenting only these lineups to subjects are
considered to be bad practices as subjects will lose interest quickly.
Therefore, we plan to collect 6 more evaluations on the 279 lineups with
uniform fitted values, result in
\((36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3 \times 6) / (20-2) = 133\)
subjects recruited for data collection period III.

@@

Subjects for all three data collection periods are recruited from an
crowdsourcing platform called Prolific \citep{palan2018prolific}.
Prescreening procedure is applied during the recruitment, subjects are
required to be fluent in English, with \(98\%\) minimum approval rate
and 10 minimum submissions in other studies.

@@

There are 2880, 2700 and 1674 lineups evaluation made by 160, 150 and
133 subjects recruited for data collection periods I, II and III
respectively. In the total of 7974 lineup evaluations, 3744 use lineups
produced by the non-linearity model, and 4230 use lineups produced by
the heteroskedasticity model. Besides, there are 886 attention checks
and 720 evaluations on null lineups needed for the estimate of
\(\alpha\) not included in the analysis. The collated dataset is
provided in \texttt{vi\_survey} of the \texttt{visage} \texttt{R}
package.

@@

\caption{Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. Each power curve of the uniform distribution is surrounded by a grey line to indicate it is the baseline in its group. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power of visual tests for non-linearity patterns in residual plots. For heteroskedasticity patterns, normal and lognormal distributions produce lower power for both types of tests.}\label{fig:different-x-dist-poly-power}
\end{figure}

@@

This paper has demonstrated that conventional residual-based statistical
tests are more sensitive to departures from assumptions for residuals
than visual tests evaluated by humans in the diagnostics of linear
regression models. An experiment is conducted in three data collection
periods with two simulation models designed for non-linearity and
heteroskedasticity model defects being applied. Methods for obtaining
the \(p\)-value of visual tests proposed by
\citet{vanderplas2021statistical} are extended to allowed for multiple
selections in a lineup protocol.

@@

Throughout the three data collection periods of the human subject
experiment we conducted, residual plots rejected by visual tests are
rarely not rejected by conventional tests, but departures of residuals
that are of little practical sense to humans will often be alarmed by
conventional tests, supporting the common guidance given by experts to
utilize graphical representations of data in model diagnostics.

We have also found that residual-based conventional tests relying on a
user-parameterized test formula, such as the RESET test, will suffer
from a significant decrease in power for detecting certain residual
departures intended to be tested but not covered by the test formula.
This can not be avoided without prior knowledge of their functional
forms, which is usually obtained by plotting the residuals. On the other
hand, visual tests do not rely on such information and a collection of
departures can be tested simultaneously.

fitted value distribution

orientation of heter shape

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  how does this apply more broadly than simple regression
\end{enumerate}

recommend residual vs fitted values a. measure uncertainty b.
systemically miss some structure

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  where does this lead? Computer vision residual plot reading
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  put \#eval in appendix
\item
  examine batch effect in appendix
\item
  compute the power of RESET test with different orders (considering
  dof) (focus on simple pattern possibly?)
\end{enumerate}
